\begin {rubric} {Experience}

\entry* [11/2014-\ldots]
\textbf {Software Engineer at Google}

Worked on search quality evaluation, developing internal pipelines and
tools that support search engineers and analysts to make data based
decisions. The robust, highly scalable pipelines ingested multi PB of
data in a low-latency environment written in highly performant C++.

I hosted two interns and led a project with another engineer. This
project asked search users about their experience using surveys. These
surveys were configured by search engineers and analysts to target
specific features and to ask specific questions. The search
infrastructure has strict requirements in latency so that any
significant increase in latency must be justified, which forces
engineers to produce the lowest latency possible code that gets the
work done.


\entry* [12/2012-09/2014]
\textbf {Software Development Engineer at Microsoft}

Developed experiences for segments on Bing.  Created ideas of
experiences for new segments, developed these ideas, analyzed the
impact of the changes in production and maintained the code in C\#.

\entry* [08/2012-05/2014]
\textbf {Owner at \emph{Juris Correspondente}}

Created a website for lawyer service announcements using crawled
information from other websites, as well as users from the
website. Worked with Ruby on Rails, Python and Haskell.

\entry* [10/2012-12/2012]
\textbf {Professor at \emph{Centro Universitário de Formiga} (UNIFOR-MG)}

$\bullet$ Formal languaguages and abstract machines

$\bullet$ Paradigms of programming languages

$\bullet$ Computer Science students

\entry* [02/2012-11/2012]
\textbf {Substitute Professor at \emph{Universidade Federal de Ouro Preto} (UFOP)}

Computer Programming 1 using Scilab for Engineering students.

\entry* [06/2011-03/2012]
\textbf {Software engineer on Zunnit}

$\bullet$ Worked with C++ using Google Test and Log4CXX, Python and Shell Script.

$\bullet$ Led the team that created the architecture for the recommendation
system.

$\bullet$ Compared several distributed NoSQL storage options, including
Cassandra, Voldemort, memcached and Tokyo Cabinet.

$\bullet$ Came up with a solution for automatic deployment of our systems basing
on my past experience with Debian.

\entry* [2005-2011]
\textbf {Debian packaging}

$\bullet$ Haskell library packaging, development of the Haskell-related Debian
infrastructure and porting of GHC to other architectures and KFreeBSD.

$\bullet$ Debian developer since January 2010, maintainer since July 2005 and
user since 2002.

\entry* [05/2012-08/2010]
\textbf{Google Summer of Code}

Implemented the algorithm of garbage collection called Immix on GHC.

\textit{Mentor} Simon Marlow

\textit{Organization} Haskell.org

\entry* [10/2008-08/2009]
\textbf {Internship at Holoscópio}

$\bullet$ Researched about software that generate distributions for embbeded
devices, comparing options like Gentoo, Debian, Emdebian and Busybox.

$\bullet$ Developed a graphical application for the customization of Debian
distributions in Python and GTK.

$\bullet$ Worked on getting GPS positions and showing it on maps, using C with libgps and libchamplain.

%% \subrubric {Computação}
\entry* [08/2004-10/2007]
\textbf {Undergraduate Research on Geoprocessing}

$\bullet$ \emph{Empresa de Informática de Belo
    Horizonte} (Prodabel) and \emph{Instituto Nacional
  de Pesquisas Espaciais} (INPE)

$\bullet$ Formalized in Haskell a modeling proposal for urban objects.

\end {rubric}
